---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

#Libraries
```{r}
detach(package:plyr)
library(haven)
library(labelled)
library(readxl)
library(tidyverse)
library(hrbrthemes)
library(dplyr)
library(foreign)
library(sjlabelled)
library(readr)
library(tibble)
library(summarytools)
library(plyr)
library(MASS)
library(cli)
library(essurvey)
library(devtools)
library(survey)


```


#Importing Data, Creating Dictionary
```{r}

devtools::install_github("ropensci/essurvey")
 
set_email("halilibrahimergul55@gmail.com")
show_countries()

show_country_rounds("Germany")

ess9 <-
  import_country(
    country = "United Kingdom",
    rounds = 9
    )

germ <-
  import_country(
    country = "Germany",
    rounds = 9
    )

ess9 <- rbind(ess9, germ)

sum(is.na(ess9$gndr))
colnames(ess9)

dict_ess9 <-labelled::generate_dictionary(ess9)

```

# EDA on Variables
```{r}
# Dependent Variables: System responsiveness (psppsgva, , cptppola, actrolga (subjective))
 # İndependent = gndr, clsprty (feel close to a party  yes or no), prtclcgb (which party feel closer to)
# How interested in politics (polintr), How satisfied with present state of economy in country (stfeco), 
# How satisfied with the way democracy works in country (stfdem)
# Member of a group discriminated against in this country (dscrgrp)
# Citizen of country (ctzcntr)
#  age (agea)
# 	Highest level of education (edulvlb) ***** educgb1, educgb2
# Household's total net income, all sources (hinctnta)
# Any period of unemployment and work seeking lasted 12 months or more (uemployment)
# Trust in country's parliament, Trust in politicians, Trust in political parties (trstprl, trstplt, trstprt)

cor(ess9$psppsgva, ess9$psppipla, use = "pairwise.complete.obs")

sum(is.na(ess9$psppipla))

#Replacing NAs with Median values
ess9$psppsgva[is.na(ess9$psppsgva)] <- median(ess9$psppsgva, na.rm = TRUE)
ess9$psppipla[is.na(ess9$psppipla)] <- median(ess9$psppipla, na.rm = TRUE)
ess9$agea[is.na(ess9$agea)] <- mean(ess9$agea, na.rm = TRUE)

#Factorizing haven values? (for ordinal and nominal different)
is.factor(ess9$psppsgva)
class(ess9$gndr)
class(ess9$psppipla)
ess9$psppsgva <- base::as.ordered(ess9$psppsgva)
ess9$psppipla <- base::as.ordered(ess9$psppipla)
ess9$actrolga <- base::as.ordered(ess9$actrolga)
ess9$cptppola <- base::as.ordered(ess9$cptppola)
ess9$psppsgva <- base::as.numeric(ess9$psppsgva)
ess9$psppipla <- base::as.numeric(ess9$psppipla)
ess9$actrolga <- base::as.numeric(ess9$actrolga)
ess9$cptppola <- base::as.numeric(ess9$cptppola)
ess9$gndr <- base::as.factor(ess9$gndr)
ess9$agea <- base::as.numeric(ess9$agea)
ess9$clsprty <- base::as.factor(ess9$clsprty)
ess9$polintr <- base::as.factor(ess9$polintr)
ess9$stfeco <- base::as.ordered(ess9$stfeco)
ess9$stfdem <- base::as.ordered(ess9$stfdem)
ess9$dscrgrp <- base::as.factor(ess9$dscrgrp)
ess9$ctzcntr <- base::as.factor(ess9$ctzcntr)
ess9$eisced <- base::as.factor(ess9$eisced)
ess9$hinctnta <- base::as.ordered(ess9$hinctnta)
ess9$prtvtcgb <- base::as.factor(ess9$prtvtcgb)
ess9$prtclcgb <- base::as.factor(ess9$prtclcgb)
ess9$lrscale <- base::as.factor(ess9$lrscale)
ess9$uemp12m <- base::as.factor(ess9$uemp12m)
ess9$dscrgrp <- base::as.factor(ess9$dscrgrp)
ess9$stfeco <- base::as.numeric(ess9$stfeco)


ess9$dscrgrp


ess9$edulvlb

ctzcntr


str(ess9$ctzcntr)

class(ess9$lrscale)

sum(is.na(ess9$ctzcntr))


names(ess9$dscrgrp)

length(object) # number of elements or components
str(object)    # structure of an object
class(object)  # class or type of an object
names(object)  # names

newobject <- edit(object) # edit copy and save as newobject
fix(object)               # edit in place



# Labeling gender and partisanship variables (BUNU da SOR)
ess9$gndr <- factor(ess9$gndr,
levels = c(0,1),
labels = c("Male", "Female"))

ess9$clsprty <- factor(ess9$clsprty,
levels = c(1,0),
labels = c("Yes", "No"))

unique(ess9$clsprty)


ess9 %>% 
  group_by(gndr) %>% 
  summarise(mean(agea))

ess9 %>%
  count(psppsgva)

ess9 %>% 
  count(clsprty)

ess9 %>%
  group_by(prtclcgb) %>% 
  summarise(mean = mean(psppsgva, na.rm = TRUE)) %>% 
  arrange(desc(mean))

# 1 - freq() : Frequency Tables

freq(ess9$eisced, style = "rmarkdown")
freq(ess9$prtclcgb, style = "rmarkdown")

# 2 - ctable() : Cross-Tabulations

ctable(x = ess9$partyclose,
       y = ess9$cntry,
       prop = "c", chisq= TRUE, na.rm = TRUE)


# 3 - descr() : Descriptive Univariate Stats
descr(ess9$agea, stats = c("mean", "sd", "min", "med", "max"), transpose = TRUE, 
      headings = TRUE, style = "rmarkdown")

str(ess9$psppsgva)

class(ess9$gndr)
unique(ess9$psppsgva)


# Visuals

cor(ess9$psppsgva, ess9$psppipla, use = "pairwise.complete.obs")
cor(ess9$actrolga, ess9$cptppola, use = "pairwise.complete.obs")

cor(ess9$psppsgva, ess9$actrolga, use = "pairwise.complete.obs")


ggplot(ess9, aes(x = psppsgva)) +
  geom_bar()
ggplot(ess9, aes(x = actrolga)) +
  geom_bar()
ggplot(ess9, aes(x = cptppola)) +
  geom_bar()

actrolga

cptppola

ggplot(ess9, aes(x = psppipla)) +
  geom_bar()

ggplot(ess9, aes(x = gndr, fill = gndr)) +
  geom_bar()

ess9 %>% 
  group_by(gndr) %>% 
  summarise(n = count(gndr))

ess9 %>%
  group_by(clsprty) %>% 
  summarise(n = count(clsprty))

ggplot(ess9, aes(x = clsprty, fill = clsprty)) +
  geom_bar()

ggplot(ess9, aes(x = polintr, fill = polintr)) +
  geom_bar()

ess9 %>%
  group_by(polintr) %>% 
  summarise(n = count(polintr))

ggplot(ess9, aes(x = stfeco, fill = stfeco)) +
  geom_histogram(stat="count")

ggplot(ess9, aes(x = stfdem, fill = stfdem)) +
  geom_bar()

ggplot(ess9, aes(x = dscrgrp, fill = dscrgrp)) +
  geom_bar()

ess9 %>%
  group_by(dscrgrp) %>% 
  summarise(n = count(dscrgrp), percent =)

ggplot(ess9, aes(x = ctzcntr, fill = ctzcntr)) +
  geom_bar()

ggplot(ess9, aes(x = edulvlb, fill = edulvlb)) +
  geom_bar()



```


#Recoding Variables
```{r}
# Education variable "ess9$edulvlb" sucks. Years of education (eduyrs) can be used directly, although the variable is not the best indicator of educational attainment in the ESS. Best eduation measure is "eisced". Recode ‘eisced’ into a new variable with three levels: primary (1,2), secondary (3,4) and tertiary (5,6,7). Create dummy indicators for the three levels of education.

# income 10 decile üzerinden ölçülüyor, ilginç. The variable ‘hinctnta’, ‘Household’s net income, all sources’, is a variable with ten categories, in addition to missing. Our suggestion is to simplify this and compute a new variable, 'hinc4', with the following values: low income - medium income - high income - missing.  Compute dummies for each of the four values on 'hinc4'

unique(ess9$eisced)


ggplot(ess9, aes(x = educ, fill = educ)) +
  geom_bar()

# Recoding new variable : from eisced to "educ"

ess9$educ = revalue(ess9$eisced, c("1" = "1", "2" = "1", "3" = "2" , "4" = "2", "5" = "2" , "6" = "3", "7" = "3"))



freq(ess9$hhincome, style = "rmarkdown")
freq(ess9$educ, style = "rmarkdown")
class(ess9$educ)
sum(is.na(ess9$educ))

# Recoding new variable: from hinctnta to "hhincome"

class(ess9$hinctnta)

ess9$hhincome = revalue(ess9$hinctnta, c("1" = "1", "2" = "1", "3" = "1" , "4" = "2", 
                                         "5" = "2" , "6" = "2", "7" = "2", "8" = "3" ,"9" = "3","10" = "3"))

ggplot(ess9, aes(x = hhincome, fill = hhincome)) +
  geom_bar()


sum(is.na(ess9$hhincome)) # 350 NA var.
unique(ess9$hhincome) #NA'leri ne yapacağız?

freq(ess9$hhincome, style = "rmarkdown")

#Centered or squared age

sum(is.na(ess9$agea)) # 16 tane NA var. Bunları halletmeden centered ve squared hesaplasam sıkıntı olur mu?

ess9$agea[is.na(ess9$agea)] <- median(ess9$agea, na.rm = TRUE)

hist(ess9$agea)

mean(ess9$agea, na.rm = TRUE)

ess9$age_cent <- ess9$agea - 50.97
ess9$agecent_sq <- ess9$age_cent ^ 2

hist(ess9$age_cent)
hist(ess9$agecent_sq)

# Gender: 1 is female, 0 is male

unique(ess9$gndr)
class(ess9$gndr)

freq(ess9$gndr, style = "rmarkdown")

ess9$gender = revalue(ess9$gndr, c("1" = "0", "2" = "1"))

freq(ess9$gender, style = "rmarkdown")

class(ess9$gender)

# Party Orientation: prtclcgb (bazılarının sayısı çok az, etklememesi için onları da mı other'a atmalı ??) and 

class(ess9$prtclcgb)

freq(ess9$prtclcgb, style = "rmarkdown")

ess9$party = revalue(ess9$prtclcgb, c("1" = "1", "2" = "2", "3" = "3", "4" = "5", "5" = "5","6" = "4", "7" = "5", "8" = "5", "9" = "5", "10" = "5", "11" = "5", "12" = "5", "13"= "5", "15" = "5" , "19" = "5"))


ggplot(ess9, aes(x = party, fill = party)) +
  geom_bar()

freq(ess9$party, style = "rmarkdown")
# 1--- Conservative
# 2--- Labor
# 3--- Liberal Democrat
# 4--- Green Party
# 5--- OTHER

#Feel closer to any party? (clsprty, 1 = yes, 2 = no)

freq(ess9$clsprty, style = "rmarkdown")

ess9$partyclose = revalue(ess9$clsprty, c("1" = "1", "2" = "0"))

ess9$partyclose <- fct_relevel(ess9$partyclose, "0", "1")

freq(ess9$partyclose, style = "rmarkdown")


#Recoding new variable "polsscale" from "lrscale". Left and Right ( 1 den 10'a skala, doğrudan eklesem problem olmaz herhalde)

sum(is.na(ess9$lrscale))
unique(ess9$lrscale)

freq(ess9$lrscale, style = "rmarkdown")

ggplot(ess9, aes(x = lrscale, fill = lrscale)) +  # Bu dağılıma bakılarak 3'e bölünebilir: Left (1), middle(2), right(3)
  geom_bar()


descr(ess9$lrscale, stats = c("mean", "sd", "min", "med", "max"), transpose = TRUE, 
      headings = TRUE, style = "rmarkdown")


ess9$polsscale = revalue(ess9$lrscale, factor(c("0" = "1", "1" = "1", "2" = "1", "3" = "1", "4" = "1", "5" = "2", "6" = "3", "7" = "3", "8" = "3", "9" = "3", "10" = "3"), ordered = FALSE))

ess9$polsscale <- relevel(ess9$polsscale, ref = "1")

freq(ess9$discrim, style = "rmarkdown")

ggplot(ess9, aes(x = polsscale, fill = polsscale)) +
  geom_bar()


ess9$polsscale <- factor(ess9$polsscale, ordered = FALSE )

class(ess9$polsscale)
levels(ess9$polsscale)


# How satisfied with present state of economy in country: stfeco (0 to 10) #### SOOOOOR!

freq(ess9$stfeco, style = "rmarkdown")


# How satisfied with the way democracy works in country: stfdem (0 to 10)



# Unemp

ess9$unemp = revalue(ess9$uemp12m, c("1" = "1", "2" = "0"))
freq(ess9$unemp, style = "rmarkdown")



# Member of a group discriminated against in this country (dscrgrp)

ess9$discrim = revalue(ess9$dscrgrp, c("1" = "1", "2" = "0"))
freq(ess9$discrim, style = "rmarkdown")

ess9$discrim <- relevel(ess9$discrim, ref = "0") # For reference category to  be 0

ess9$partyclose <- relevel(ess9$partyclose, ref = "0")



# Recoding variable: polintr

ess9$polintr <- base::as.factor(ess9$polintr)

freq(ess9$polintr, style = "rmarkdown")

ess9$polintr <- fct_recode(ess9$polintr, "1" = "4", "2" = "3", "3" = "2", "4" = "1")

ess9$polintr <- fct_relevel(ess9$polintr, "1", "2", "3", "4")

freq(ess9$polintr, style = "rmarkdown")




ess9$polintr <- relevel(factor(ess9$polintr), ref = "1")

# How emotionally attached to [country]--- atchctr (0 to 10)

class(ess9$atchctr)

ess9$atchctr <- base::as.numeric(ess9$atchctr)

```


#Creating Index variables for external efficacy and trust
```{r}
# KMO The Kaiser-Meyer-Olkin (KMO) used to measure sampling adequacy is a better measure of factorability.
library(psych)
library(ltm)
library(corrplot)
library("psych")
library(ggplot2)
library(car)

# For Outcome variable: psppsgva, psppipla (missingleri ne yapmalı?)
outcome$psppsgva <- base::as.numeric(outcome$psppsgva)
outcome$psppipla <- base::as.numeric(outcome$psppipla)

outcome <- ess9 %>%
  dplyr::select(c(psppipla, psppsgva))

outcome <- na.omit(outcome)

# CA is 0.756; quite decent
cronbach.alpha(outcome,CI=TRUE, standardized=TRUE)

#The Kaiser-Meyer-Olkin (KMO)
KMO(r = cor(outcome))

#Bartlett’s Test of Sphericity
cortest.bartlett(outcome)

#The Number of Factors to Extract: Parallel Analysis
fa.parallel(outcome)

#Factor analysis using the factanal method
factanal.none <- factanal(outcome, factors=1, scores = c("regression"), rotation = "varimax")
print(factanal.none)

#PCA: You obtain 2 principal components. Each of these explains a percentage of the total variation in the dataset. That is to say: PC1 explains 80% of the total variance which means that most of the information in the dataset (2 variables) can be encapsulated by just that one Principal Component.

library(devtools)
library(ggbiplot)

outcome.pca <- prcomp(outcome, center = TRUE,scale. = TRUE)

summary(outcome.pca)

str(outcome.pca)

ggbiplot(outcome.pca, circle = TRUE)

# compute total variance
variance = outcome.pca$sdev^2 / sum(outcome.pca$sdev^2)

#scree plot
qplot(c(1:2), variance) +
  geom_line() +
  geom_point(size=4)+
  xlab("Principal Component") +
  ylab("Variance Explained") +
  ggtitle("Scree Plot") +
  ylim(0, 1)

#Package for PCA visualization

install.packages("factoextra")
library(factoextra)

#Visualize eigenvalues (scree plot). Show the percentage of variances explained by each principal component.
fviz_eig(outcome.pca)

fviz_pca_ind(outcome.pca,
             col.ind = "cos2", # Color by the quality of representation
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = FALSE     # Avoid text overlapping
             )

#Graph of variables. Positive correlated variables point to the same side of the plot. Negative correlated variables point to opposite sides of the graph.

fviz_pca_var(outcome.pca,
             col.var = "contrib", # Color by contributions to the PC
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     # Avoid text overlapping
             )

```

#Combining new indexes
```{r}
freq(ess9$psppsgva, style = "rmarkdown")

#replacing NAs
ess9$psppipla <- base::as.numeric(ess9$psppipla)
ess9$psppsgva <- base::as.numeric(ess9$psppsgva)
ess9$efficacy <- base::as.numeric(ess9$efficacy)

efficacy


ess9$psppsgva[is.na(ess9$psppsgva)] <- median(ess9$psppsgva, na.rm = TRUE)
ess9$psppipla[is.na(ess9$psppipla)] <- median(ess9$psppipla, na.rm = TRUE)

# For Outcome variable: psppsgva, psppipla----------- efficacy
sum(is.na(ess9$psppsgva)) #30
sum(is.na(ess9$psppipla)) #25
sum(is.na(ess9$efficacy))

ess9 <- ess9 %>% 
  mutate(efficacy = (psppsgva + psppipla) / 2) 

ggplot(ess9, aes(x = efficacy)) +
  geom_bar()

ess9$efficacy <- base::as.factor(ess9$efficacy)
ess9$stfeco <- base::as.numeric(ess9$stfeco)
ess9$stfdem <- base::as.numeric(ess9$stfdem)


ggplot(ess9, aes(x = efficacy, fill = efficacy)) +
  geom_bar(aes(y = (..count..)/sum(..count..))) +
   scale_y_continuous(labels=scales::percent) +
  ylab("relative frequencies")

```


```{r}
# Building Model
```{r}


library(foreign)
library(MASS)
library(Hmisc)
library(reshape2)

atchctr

ess9$polintr <- base::as.numeric(ess9$polintr) #bunu böyle numeric eklesem ne olur?

# model 1 AIC: 13718.73 
model1 <- lm(efficacy ~ partyclose + polsscale + agea + gender + hhincome + educ + discrim + polintr + atchctr, data = ess9)

# model 2 AIC: 2389.576 (but soo missings are deleted)
model2 <- polr(efficacy ~ partyclose + age_cent + gender + hhincome + educ + discrim, data = ess9, Hess=TRUE)

# Model 3 AIC: 13019.45
model3 <- polr(efficacy ~ polsscale + age_cent + gender + hhincome + educ + discrim + polintr+ atchctr, data = ess9, Hess=TRUE)

summary(model1)

#coefficient table
(ctable <- coef(summary(model1)))

#Adding P-value
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

(ctable <- cbind(ctable, "p value" = p))

#Confidence Intervals For the Model
(ci <- confint(model1))


# The coefficients from the model can be somewhat difficult to interpret because they are scaled in terms of logs. Another way to interpret logistic regression models is to convert the coefficients into odds ratios.

## odds ratios
exp(coef(model1))

## OR and CI
exp(cbind(OR = coef(model1), ci))


```


#Trust and Effiacy are almost Redundant !!!
```{r}


ess9$efficacy <- base::as.factor(ess9$efficacy)


cor(ess9$efficacy,ess9$trustin, use = "pairwise.complete.obs")

cron <- ess9 %>% 
  dplyr::select(c(efficacy,trustin))

cron <- na.omit(cron)

cronbach.alpha(cron,CI=TRUE, standardized=TRUE)


#PCA
cron.pca <- prcomp(cron, center = TRUE,scale. = TRUE)

summary(cron.pca)

str(cron.pca)

ggbiplot(cron.pca, circle = TRUE)

# compute total variance
variance = cron.pca$sdev^2 / sum(cron.pca$sdev^2)

#scree plot
qplot(c(1:2), variance) +
  geom_line() +
  geom_point(size=4)+
  xlab("Principal Component") +
  ylab("Variance Explained") +
  ggtitle("Scree Plot") +
  ylim(0, 1)


```


#Country Comparison
```{r}
ess9$efficacy <- base::as.numeric(ess9$efficacy)

ess9 %>%
  filter(cntry == "GB") %>% 
  ggplot(aes(efficacy, fill = efficacy)) +
  geom_bar()

ess9 %>%
  filter(cntry == "DE") %>% 
  ggplot(aes(efficacy)) +
  geom_bar()

library(tidyverse)
library(ggpubr)
library(rstatix)


ess9 %>%
  group_by(cntry) %>%
  get_summary_stats(efficacy, type = "mean_sd")


# Save the data in two different subset data for OLS

de <- subset(ess9, cntry == "DE")

uk <- subset(ess9, cntry == "GB")

#OLS model for UK

modeluk <- lm(efficacy ~ partyclose + polsscale + agea + gender + hhincome + educ + discrim + polintr + atchctr, data = uk)

#OLS model for Germany
modelde <- lm(efficacy ~ partyclose + polsscale + agea + gender + hhincome + educ + discrim + polintr + atchctr, data = de)

stargazer(modeluk, modelde)
# Compute t-test
res <- t.test(efficacy ~ cntry, data = ess9)
res


stat.test2 <- ess9 %>%
  t_test(efficacy ~ cntry, var.equal = TRUE) %>%
  add_significance()
stat.test2





# Coefficient Plot

plot(coef(model1), 1:15, yaxt = 'n', pch = 18,
     xlim = c(min(confint(model1)), max(confint(model1))),
     ylab = '', xlab = 'Estimates')
segments(x0 = confint(model1)[,1], x1 = confint(model1)[,2],
         y0 = 1:4, y1 = 1:4)
abline(v=0, lty = 3)
axis(2, at = 1:4,
     tick = F, labels = c(expression(beta['0']),
                          expression(beta['1']),
                          expression(beta['2']),
                          expression(beta['3'])),las = 1)
library(broom)
coef = tidy(model1, conf.int = T)
coef
ggplot(coef, aes(term, estimate))+
  geom_point()+
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high))+
  labs(title = "Coefficients of a linear regression model")


#Note that the intercept is omitted by default because it often distorts the scale and generally isn’t of theoretical interest.
plot_summs(model1, scale = TRUE, inner_ci_level = .95)

plot_summs(modelde, scale = TRUE, inner_ci_level = .95)

plot_summs(modeluk, scale = TRUE, inner_ci_level = .95)

```




